---
title: "Learn R: Resources"
author: "Anders Swanson"
date: November 1, 2018
output:
    html_document:
        toc: true
        toc_float: true
---


```{r setup, include=FALSE, results='hide', warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
chooseCRANmirror(graphics=FALSE, ind=1)
```

## Resources

### Do your own project!

I can emphasize this enough. I know you have an exam to pass, but this is the best way to get familiar with the language. Find a dataset and work with it!

### Documentation Lookup

Lookup function doumentation with `?`.

Don't know what `readr`'s  `read_csv()` function does? Look it up by running `?read_csv`!

### R for Data Science

Hadley Wickham's book, available for free!
[https://r4ds.had.co.nz/](https://r4ds.had.co.nz/)

### DataCamp

[https://www.datacamp.com/](https://www.datacamp.com/)

Lots of great classes here, I like going here when I have a new project to learn:
- [Tidyverse Skill Track](https://www.datacamp.com/tracks/tidyverse-fundamentals)
- [Quantitative Risk Management in R](https://www.datacamp.com/courses/quantitative-risk-management-in-r)

Sign up for [Visual Studio Dev Essentials](https://visualstudio.microsoft.com/dev-essentials/) to get 3 months of Datacamp for free!

### swirlR

Its like datacamp but inside of R Studio

```{r, eval = FALSE}

install.packages("swirl")

library(swirl)

swirl()

swirl::install_course("R Programming") # general into to R
swirl::install_course("Exploratory Data Analysis") # using ggplot2
swirl::install_course("Getting and Cleaning Data") #  dplyr, tidyr, lubridate
```

### RStudio Cheatsheets

I highly recommend that you print these out and put them in a binder. They'll be immensely helpful
[https://www.rstudio.com/resources/cheatsheets/](https://www.rstudio.com/resources/cheatsheets/)


### UC Business Analytics R Programming Guide

Bradley Boehmke at University of Cincinnati has written a very comprehensive into to R.

In particular his [predictive analytics guide](http://uc-r.github.io/predictive) is great for you guys, I recommend using:
- regression trees & bagging
- random forest
